Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-11-04 Paper.tex
Add files via upload

On the other hand, one of the major problems with this approach has to do
with ETH-fiat exchange volatility
(\textit{see figure 7}), anyway, including
a feature to regulate minute price in the state channel
contract and taking into account gas prices can adjust
in order to properly
represent computation, bandwidth and storage costs this
problem can be completely avoided.

@@

\begin{center}
%\begin{figure}[h]
%  \centering
  \includegraphics[keepaspectratio, width=0.5\textwidth]{images/maxresdefault.eps}
%  \caption{Figura 2. Raspberry Pi 3 Modelo B. Fuente: [Raspberry 18]}
%\end{figure}
\\
Figure 10. A demo video screenshot.
\\
\end{center}
\vspace{0.15cm}
Finally, the following hyperlinks to Etherscan show the Ethereum transactions done:
\newline\newline

>>>>

On the other hand, one of the major problems with this approach has to do
with ETH-fiat exchange volatility
(\textit{see figure 10}), anyway, including
a feature to regulate minute price in the state channel
contract and taking into account gas prices can adjust
in order to properly
represent computation, bandwidth and storage costs this
problem can be completely avoided.

\begin{center}
%\begin{figure}[h]
%  \centering
  \includegraphics[keepaspectratio, width=0.5\textwidth]{images/ethcurrentprice-sourcecoinbase-y.eps}
%  \caption{Figura 2. Raspberry Pi 3 Modelo B. Fuente: [Raspberry 18]}
%\end{figure}
\\
Figure 10. ETH price (August 11, 2019) [23].
\\
\end{center}

@@

\begin{center}
%\begin{figure}[h]
%  \centering
  \includegraphics[keepaspectratio, width=0.5\textwidth]{images/maxresdefault.eps}
%  \caption{Figura 2. Raspberry Pi 3 Modelo B. Fuente: [Raspberry 18]}
%\end{figure}
\\
Figure 11. A demo video screenshot.
\\
\end{center}
\vspace{0.15cm}
Finally, the following hyperlinks to Etherscan show the Ethereum transactions done:
\newline\newline
